The \emph{FThresholds} package for \emph{Macaulay2}

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
minor changes to intro of FThresholds paper

Along these lines, the notion of the \emph{$F$-pure threshold} was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.  
The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.  
Furthermore, the more general \emph{$F$-thresholds} was also introduced, a family that contains the $F$-pure threshold. 
These numerical invariants are typically very difficult to calculate in general, and have been the 
focus of intense study over the past fifteen years.
This \emph{Macaulay2} package is centered around calculating 
and estimating the $F$-pure threshold and other $F$-thresholds.

There are three main sections in this paper, describing the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}. 
\begin{itemize}
\item \autoref{sec.Nu} describes the methods implemented for approximating the $F$-pure threshold and other $F$-thresholds.  
\item \autoref{sec.IsFPT} describes functionality for determining whether a given number is the $F$-pure threshold, or more generally, an $F$-jumping exponent.
\item \autoref{sec.FPT} describes the function {\tt fpt} for estimating and computing $F$-pure thresholds, and how it works.
\end{itemize}

>>>>

Along these lines, the notion of the \emph{$F$-pure threshold} was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.  
The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.  
Furthermore, the more general \emph{$F$-thresholds} was also introduced, a family that contains the $F$-pure threshold. 
These numerical invariants are typically very difficult to calculate, and due to their significance, have been the 
focus of intense study over the past fifteen years.
This \emph{Macaulay2} package is centered around calculating 
and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.

There are three main sections in this paper, which describe and illustrate the functionality implemented in the package \emph{FThresholds}. 
\begin{itemize}
\item \autoref{sec.Nu} describes the methods implemented for approximating the $F$-pure threshold and other $F$-thresholds.  
\item \autoref{sec.IsFPT} explains the package's functionality for determining whether a given number is the $F$-pure threshold, or more generally, an $F$-jumping exponent.
\item \autoref{sec.FPT} is focused on the features of the function {\tt fpt} for estimating and computing $F$-pure thresholds, and how it works. 
\end{itemize}
